---
title: "02-recreate_base_model"
output: html_document
---

```{r setup, include=FALSE}

library(dplyr)
library(DescTools)

knitr::opts_chunk$set(echo = TRUE)

box::use(here[here])
options(box.path = here())

box::use(
  tibble[as_tibble],
  r / load_data,
  r / utils
)
```

```{r}
df <- load_data$ess1()
```


```{r}
reg_df <- df %>%
  transmute(
    av = case_when(
      impcntr %in% c(
        "Allow some",
        "Allow many to come and live here"
      ) ~ 1,
      impcntr %in% c(
        "Allow a few",
        "Allow none"
      ) ~ 0
    ),
    wght = pweight * dweight,
    age = agea,
    gender = gndr,
    years_of_schooling = eduyrs,
    country = cntry,
    native = relevel(brncntr, "No"),
    minority_area = as.numeric(acetalv),
    partisan_right = lrscale,
    income = hinctnt
  )
```

```{r}

orig_data_model8 <- list(
  names = c("years_of_schooling", "age", "genderFemale", "income", "nativeYes", "minority_area", "partisan_right"),
  effect = c(0.024, -0.002, 0.011, 0.014, -0.087, 0.031, -0.023),
  se = c(0.002, 0.000, 0.012, 0.003, 0.020, 0.008, 0.003)
)

model_8 <- tibble::as_tibble(orig_data_model8)
```

# Models
## recreated model

```{r}
formula_simple_model <- as.formula("
  av ~ years_of_schooling +
  age +
  gender +
  income +
  native +
  minority_area +
  partisan_right +
  country
  ")

model <- glm(
  formula_simple_model,
  family = binomial(link = "probit"),
  weights = reg_df$wght,
  data = reg_df,
  x = TRUE
)
```

```{r}
summary(model)
```
```{r}
nobs(model)
logLik(model)
PseudoR2(model)
```


```{r}
res <- erer::maBina(model)

our_model <- res$out %>%
  mutate(names = row.names(res$out)) %>%
  filter(!grepl("^country|^\\(", names)) %>%
  left_join(model_8, by = "names", suffix = c("", ".orig")) %>%
  mutate(
    effect_diff = effect - effect.orig,
    diff_ratio = round(abs(abs(effect_diff) / effect.orig), 2)
  ) %>%
  select(names, effect, effect.orig, effect_diff, diff_ratio)


our_model
```

## model with additional interaction term

This interaction term is mentioned in a footnote in the article.
It does not seem to make sense here but gets the gender (and income) marginal effects way closer to the reported size.
Additionally: The gender effect is not significant anymore (as it should not be -- regarding to the article) if the interaction term is included in the model.

```{r}
formula_wrong_but_closer_model <- as.formula("
  av ~ years_of_schooling +
  age +
  gender +
  income +
  native +
  minority_area +
  partisan_right +
  country +
  gender * income
  ")

model <- glm(
  formula_wrong_but_closer_model,
  family = binomial(link = "probit"),
  weights = reg_df$wght,
  data = reg_df,
  x = TRUE
)

summary(model)
```

```{r}
nobs(model)
logLik(model)
PseudoR2(model)
```

```{r}
res <- erer::maBina(model)

our_model <- res$out %>%
  mutate(names = row.names(res$out)) %>%
  filter(!grepl("^country|^\\(", names)) %>%
  left_join(model_8, by = "names", suffix = c("", ".orig")) %>%
  mutate(
    effect_diff = effect - effect.orig,
    diff_ratio = round(abs(abs(effect_diff) / effect.orig), 2)
  ) %>%
  select(names, effect, effect.orig, effect_diff, diff_ratio)


our_model
```

